Defining Greatness

### 2024-12-03 paper/paper.qmd
add reference

The analysis was conducted in R [@citeR], leveraging tools from the Tidyverse [@citetidyverse], Caret [@citecaret], Arrow [@citearrow], Knitr [@citeknitr], and Testthat [@citett] packages. The code was styled using Styler [@citestyler]. The primary dataset included QB-specific data from every NFL game played since 2000, encompassing over 55 columns detailing various player performance metrics. Additional data sources were used for ESPN’s Quarterback Rating (QBR), which encapsulates QB efficiency across multiple dimensions of gameplay.

>>>>

The analysis was conducted in R [@citeR], leveraging tools from the Tidyverse [@citetidyverse], Caret [@citecaret], Arrow [@citearrow],Tinytable [@citetinytable], Knitr [@citeknitr], and Testthat [@citett] packages. The code was styled using Styler [@citestyler]. The primary dataset included QB-specific data from every NFL game played since 2000, encompassing over 55 columns detailing various player performance metrics. Additional data sources were used for ESPN’s Quarterback Rating (QBR), which encapsulates QB efficiency across multiple dimensions of gameplay.
